Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\documentclass[conference]{configs/IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multirow}
%\usepackage[table,xcdraw]{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

@@

There are two types of test cases to be tested on the system. Tirst type are cases that simulate regression by making changes that occurs at the application level by making modifications intentionally at the code level.
The first case will have an ID with an \textbf{SI} prefix signifying the \textit{Scenario-Internal}.
The second type are cases that simulate regression by increasing the number of users and load on the Load Generator. The second case will have an ID with the \textbf{SE} prefix denotes an \textit{Scenario-External}. Table IV.5 will explain the cases
system testing.

@@

\begin{table}[!htb]
	\label{testcases}
	\caption{Test Cases}
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		CheckoutService/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		CheckoutService/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		CheckoutService/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		CheckoutService/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		CheckoutService/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		CheckoutService/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		CheckoutService/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}

>>>>

\documentclass[conference]{configs/IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multirow}
%\def\tablename{Table}
%\def \figurename{Figure}

%\usepackage[table,xcdraw]{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

We first define two hypotheses namely $h_{0}$ or the null hypothesis which states that the two data samples come from the same distribution and $h_{a}$ or an alternative hypothesis which states that both sample data comes from two different distributions.

The K-S test will produce two values, namely \texttt{statistic} and \texttt{pvalue}. If the \texttt{pvalue} is less than the significant value, or alpha which can be selected from a certain constants,
then we can reject $h_{0}$ and accept $h_{a}$. If the p-value is not less than
significant value, then the next step is to compare the statistical value
and critical values. Critical value itself is a point on the test
the hypothesis that will be compared to the results of the statistical values to be used
to reject or accept the null hypothesis. If the statistical value is greater than
critical value, then we can reject h0 and accept ha or its meaning
IV-7
the two data samples come from different distributions. However, if the statistical value
smaller than the critical value, we cannot reject h0 or it means both
sample data come from the same distribution.

@@

There are two types of test cases to be tested on the system. Tirst type are cases that simulate regression by making changes that occurs at the application level by making modifications intentionally at the code level.
The first case will have an ID with an \textbf{SI} prefix signifying the \textit{Scenario-Internal}.
The second type are cases that simulate regression by increasing the number of users and load on the Load Generator. The second case will have an ID with the \textbf{SE} prefix denotes an \textit{Scenario-External}. Tab. \ref{testcases} will explain the cases
system testing.

@@

\begin{table}[!htb]
	\caption{Test Cases}
	\label{testcases}
	\centering
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		CheckoutService/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		CheckoutService/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		CheckoutService/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		CheckoutService/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		CheckoutService/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		CheckoutService/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		CheckoutService/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}

\subsection{Experiment Result}

\subsection{Overhead Testing}
